---
title: "Polling Data"
author: "Emi Cooper"
date: today
format: html
editor: visual
page-layout: full
link-citations: true
---

## Introduction

The job guarantee is widely supported across political ideologies, races, genders, and locations. Typically divisive ethical and political issues around neoliberalism, socialism, and public policy are bypassed around the question of whether a job guarantee program is favorable. The job guarantee program is a populist and reformist policy movement, that is not partisan or targeted for the advancement of one group at the expense of another. The job guarantee program provides equal access to employment for all people, providing the opportunity for economic mobility regardless of identity. This avenue through which social inequity is addressed is broadly appealing because redistribution politics are not in question. The criticisms of direct cash transfer government benefits are not applicable to a job guarantee because the employment of labor that is not typically utilized generates productivity, contributing to the growth of the economy. The aggregate economic goals that are achieved through the jobs guarantee are beneficial to people of all backgrounds and socioeconomic positions.

Support for the job guarantee has been measured through various polls, conducted in several different countries. The polls used for this paper are a Hill-Harris survey conducted in 2020, a YouGov UK poll conducted in the same year, and a French survey from 2021 by Opinionway and Institut Rousseau. All of these studies illustrate the overwhelming support for the job guarantee, and demonstrate that a diverse collection of social groups and identity categories are at least receptive, and substantially in favor of, a publicly funded jobs guarantee program.

## The United States

In a survey conducted by Hill-HarrisX among 933 registered voters, respondents were asked whether or not they support a federally funded job guarantee.

This survey was conducted online within the United States from July 3-4, 2020 among 933 registered voters by HarrisX. The sampling margin of error of this poll is plus or minus 3.2 percentage points. The results reflect a nationally representative sample of registered voters. Results were weighted for age within gender, region, race/ethnicity, income, political party, and education where necessary to align them with their actual proportions in the population.

## The United Kingdom

This poll conducted by YouGov and Neon in Great Britain on April 16-17 of 2020 asked respondents the following question: **Thinking about the financial impact of a crisis like the Coronavirus pandemic, to what extent, if at all, would you support or oppose the government introducing the following permanent measure?** **A job guarantee - where the government makes sure everyone who can work has a job.** It surveyed 2,015 people, finding majority support for the JG in all categories of gender, age, region, and political affiliation. The poll also asked the same question about the Universal Basic Income policy proposal, which garnered less support.

## France

This survey from Opinionway and Institut Rousseau with a sample size of 1,011 asked whether respondents would support a job guarantee in the ecological sector with data by gender, age, region, and population density. It found majority support for the job guarantee across all the tested demographic groups.

## Politics

```{r echo=FALSE, warning=FALSE, message=FALSE}

library(readxl)
library(tidyverse)
library(dplyr)
library(dbplyr)
library(ggplot2)
library(tidymodels)
library(ggridges)

Hill <- read_excel("~/Rstudio/EDI/pollingEDI/pollingHH2020Emi.xlsx")


library(janitor)

francePoll <-read_excel("~/Rstudio/EDI/pollingEDI/France2021Poll.xlsx")
francePoll <- clean_names(francePoll)

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

#US POLITICS

 politicalParty <- Hill |> select(Republican, Democrat, Independent, Position) |> pivot_longer(!Position,
  names_to = "Party",
  values_to = "Percentage"
)

politicalParty2 <- politicalParty |>
  mutate(n = 
           case_when(Party == "Democrat" ~ Percentage*345,
                     Party == "Republican" ~ Percentage*298,
                     Party == "Independent" ~ Percentage*270))


politicalParty2 <- politicalParty2 |> filter(Position != "Strongly support") |>
  filter(Position != "Somewhat support") |>
  filter(Position != "Strongly oppose") |>
  filter(Position != "Somewhat oppose")
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
 ggplot(politicalParty2, aes(y = Party, x = n, fill = Position)) + 
   geom_col(position = "fill")+
   labs(title = "What do parties think of the Job Guarantee?",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = "Proportion", y = "Party")
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

  ggplot(politicalPartyUK, aes(x = Party, y = Percentage, fill = Party)) +
  geom_col() +
  facet_wrap(~Position, nrow = 2) +
  guides(fill = "none") +
  labs(title = "What do UK political parties think of the Job Guarantee?",
       subtitle = "UKYouGov Survey",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = NULL, y = NULL) +
    theme_minimal()

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

#UK POLITICS

UKYouGov <- read_excel("~/Rstudio/EDI/pollingEDI/pollingUKEmi2020.xlsx")

UKYouGov <- UKYouGov |> 
  mutate(Total = Total*.01) |> 
  mutate(Conservative = Conservative*.01) |> 
  mutate(Labor = Labor*.01) |> 
  mutate(`Liberal Democrat` = `Liberal Democrat`*.01) |> 
  mutate(Remain = Remain*.01) |> 
  mutate(Leave = Leave*.01) |> 
  mutate(Male = Male*.01) |> 
  mutate(Female = Female*.01) |> 
  mutate(`18-24` = `18-24`*.01) |> 
  mutate(`25-49` = `25-49`*.01) |> 
  mutate(`50-64` = `50-64`*.01) |> 
  mutate(`65+` = `65+`*.01) |> 
  mutate(ABC1 = ABC1*.01) |> 
  mutate(C2DE = C2DE*.01) |> 
  mutate(London = London*.01) |> 
  mutate(`Rest of South` = `Rest of South`*.01) |> 
  mutate(`Midlands/Wales` = `Midlands/Wales`*.01) |> 
  mutate(North = North*.01) |> 
  mutate(Scotland = Scotland*.01)

politicalPartyUK <- UKYouGov |> select("Conservative", "Labor", "Liberal Democrat", "Position") |> pivot_longer(!Position,
  names_to = "Party",
  values_to = "Percentage"
)

politicalPartyUK <- politicalPartyUK |>
  mutate(n = 
           case_when(Party == "Labor" ~ Percentage*500,
                     Party == "Conservative" ~ Percentage*683,
                     Party == "Liberal Democrat" ~ Percentage*181))


politicalPartyUK <- politicalPartyUK |> filter(Position != "Very Supportive") |>
  filter(Position != "Supportive") |>
  filter(Position != "Unsupportive") |>
  filter(Position != "Very unsupportive")

```

The respondents belonging to the Conservative and Labor parties had the highest level of support at 73%, compared to Liberal Democrats of which only 65% support the job guarantee. 8% of the Conservative sample group are un-supportive of the job guarantee, compared to 6% of Labor and 11% of Liberal Democrats.

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot (politicalPartyUK, aes(x=Party, y=Percentage, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "What do UK political parties think of the Job Guarantee?",
       subtitle = "UKYouGov Survey",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = NULL, y = NULL) +
  scale_fill_manual(values = c(
    "Don't know" = "gray",
    "Neither supportive or unsupportive" = "black",
    "Total Supportive" = "#5F8575",
    "Total unsupportive" = "#C21E56"
  )) +
  theme_minimal()

politicalPartyUK |>
  mutate(Position = 
  case_when(
    Position == "Neither supportive or unsupportive" ~ "Neutral/Don't Know",
    Position == "Don't know" ~ "Neutral/Don't Know",
    .default = Position
            )) |>
  ggplot(aes(y = Party, x = n, fill = Position)) + 
  geom_col(position = "fill")+
  labs(title = "What do UK political parties think of the Job Guarantee?",
       subtitle = "UKYouGov Survey",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = "Proportion", y = "Party") +
   scale_fill_manual(values = c( 
    "Total unsupportive" = "#C21E56", 
    "Total Supportive" = "#5F8575", 
    "Neutral/Don't Know" = "gray" 
   )) +
  theme_minimal()

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot(politicalParty2, aes(y = Party, x = n, fill = Position)) + 
  geom_col(position = "fill")+
  labs(title = "What do parties think of the Job Guarantee?",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = "Proportion", y = "Party") +
  scale_fill_manual(values = c( 
    "NET OPPOSE" = "#D2042D", 
    "NET SUPPORT" = "#0066b2", 
    "Unsure" = "gray" 
  )) +
  theme_minimal()
```

The support, opposition, and uncertainty of the job guarantee are different across political parties. While the majority of all parties support the job guarantee, Democrats have the most support at 89%, Republicans have the most opposition at 14%, and Independents are the most unsure at 17%.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#US POLITICS

ggplot(politicalParty2, aes(x = Party, y = Percentage, fill = Party)) +
  geom_col() +
  facet_wrap(~Position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  guides(fill = "none") +
  labs(title = "What do parties think of the Job Guarantee?",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
  scale_fill_manual(values = c( 
    "Republican" = "#D2042D", 
    "Democrat" = "#0066b2", 
    "Independent" = "gray" 
  )) +
  theme_minimal()

ggplot (politicalParty2, aes(x=Party, y=Percentage, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "What do parties think of the Job Guarantee?",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
  scale_fill_manual(values = c( 
    "NET OPPOSE" = "#D2042D", 
    "NET SUPPORT" = "#0066b2", 
    "Unsure" = "gray" 
  )) +
  guides(fill = "none") +
  theme_minimal()
```

## Region

```{r echo=FALSE, warning=FALSE, message=FALSE}

#REGION USA

regionUSA <- Hill |> select(Northeast, South, Midwest, West, Position) |> 
  pivot_longer(!Position,
  names_to = "Region",
  values_to = "Percentage"
)

regionUSA <- regionUSA |> filter(Position != "Strongly support") |>
  filter(Position != "Somewhat support") |>
  filter(Position != "Strongly oppose") |>
  filter(Position != "Somewhat oppose")

ggplot (regionUSA, aes(y=Percentage, x=Region, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "Regional Breakdown",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x =NULL, y = NULL) +
  scale_fill_manual(values = c( 
    "NET OPPOSE" = "#D2042D", 
    "NET SUPPORT" = "#50C878", 
    "Unsure" = "gray" 
  )) +
  guides(fill = "none") +
  theme_minimal()
```

Support for the job guarantee dominates in all regions. The opinions across different geographical zones of the UK do not vary greatly. The greatest level of support is in Scotland at 74% and the lowest is in London at 65%. Only 9% of Londoners are against the job guarantee, and 8% of the Scotland sample oppose it.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#REGION UK

regionUK <- UKYouGov |> select("London", "Rest of South", "Midlands/Wales", 
                               "North", "Scotland", "Position") |> 
  pivot_longer(!Position,
  names_to = "Region",
  values_to = "Percentage"
)

regionUK <- regionUK |>
  mutate(n = 
           case_when(Region == "London" ~ Percentage*242,
                     Region == "Rest of South" ~ Percentage*677,
                     Region == "Midlands/Wales" ~ Percentage*437,
                     Region == "North" ~ Percentage*486,
                     Region == "Scotland" ~ Percentage*173
                    ))

regionUK <- regionUK |> filter(Position != "Very Supportive") |>
  filter(Position != "Supportive") |>
  filter(Position != "Unsupportive") |>
  filter(Position != "Very unsupportive")

regionUK |>
  mutate(Position = 
  case_when(
    Position == "Neither supportive or unsupportive" ~ "Neutral/Don't Know",
    Position == "Don't know" ~ "Neutral/Don't Know",
    .default = Position
            )) |>
  ggplot(aes(y = Position, x = Percentage, fill = Position)) +
  geom_col() +
  facet_wrap(~Region, nrow = 2, labeller = label_wrap_gen(width = 12)) +
  guides(fill = "none") +
  labs(title = "What do UK regions think of the job guarantee?",
       subtitle = "YouGov Survey Results, 2020",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = "Percentage", y = NULL) +
  scale_fill_manual(values = c(
    "Total unsupportive" = "#ef8a62", 
    "Total Supportive" = "#67a9cf",
    "Neutral/Don't Know" = "gray"
  )) +
  theme_minimal()

ggplot (regionUK, aes(x = Region, y = Percentage, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "What do UK regions think of the job guarantee?",
       subtitle = "YouGov Survey Results, 2020",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = NULL, y = NULL) +
  theme_minimal()
```

All regions support the job guarantee at high levels, between 79% and 82%. The most opposition was in the Île-de-France at 20%.

```{r echo=FALSE, warning=FALSE, message=FALSE}

#REGION FRANCE

frenchRegion <- francePoll |> select(paris, ile_de_france, province, nord_ouest,
                nord_est, sud_ouest, sud_est, position) |> 
  pivot_longer(!position,
  names_to = "Region",
  values_to = "Percentage"
)

frenchRegion <- frenchRegion |>
  mutate(n = 
           case_when(Region == "paris" ~ Percentage*42,
                     Region == "ile_de_france" ~ Percentage*186,
                     Region == "province" ~ Percentage*825,
                     Region == "nord_ouest" ~ Percentage*230,
                     Region == "nord_est" ~ Percentage*226,
                     Region == "sud_ouest" ~ Percentage*114,
                     Region == "sud_est" ~ Percentage*254
                    ))

frenchRegion <- frenchRegion |>
  mutate(Region =
           case_when(Region == "paris" ~ "Paris",
                     Region == "ile_de_france" ~ "Ile-de-France -",
                     Region == "province" ~ "Province",
                     Region == "nord_ouest" ~ "Nord Ouest",
                     Region == "nord_est" ~ "Nord Est",
                     Region == "sud_ouest" ~ "Sud Ouest",
                     Region == "sud_est" ~ "Sud Est"
           ))

frenchRegion <- frenchRegion |> filter(position != "Somewhat in favor") |>
  filter(position != "quite in favor") |>
  filter(position != "Somewhat opposed") |>
  filter(position != "quite opposed")


ggplot(frenchRegion, aes(y = position, x = Percentage, fill = position)) +
  geom_col() +
  facet_wrap(~Region, nrow = 2, labeller = label_wrap_gen(width = 12)) +
  guides(fill = "none") +
  labs(title = "What do French regions think of the job guarantee?",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = "Percentage", y = NULL) +
  scale_fill_manual(values = c(
    "Total opposed" = "#ef8a62", 
    "Total in favor" = "#67a9cf",
    "No response" = "gray"
  )) +
  theme_minimal()

ggplot (frenchRegion, aes(y=Percentage, x=Region, fill=position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "What do French regions think of the job guarantee?",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = "Percentage", y = NULL) +
  theme_minimal()
```

## Education

The sample population grouped by education level was divided between people with less than 4 years of college and those with at least 4 years of college.

```{r echo=FALSE, warning=FALSE, message=FALSE}

education <- Hill |> select("<4-year", "4-year+", "Position") |> 
  pivot_longer(!Position,
  names_to = "Education",
  values_to = "Percentage"
)

education <- education |>
  mutate(n = 
           case_when(Education == "<4-year" ~ Percentage*606,
                     Education == "4-year+" ~ Percentage*326,
                    ))
education2 <- education |> filter(Position != "Strongly support") |>
  filter(Position != "Somewhat support") |>
  filter(Position != "Strongly oppose") |>
  filter(Position != "Somewhat oppose")
 
 ggplot(education2, aes(x = Education, y = Percentage, fill = Education)) +
  geom_col() +
  facet_wrap(~Position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  labs(title = "Variations in Education Level",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
   theme_minimal()
 
 ggplot (education2, aes(x=Education, y=Percentage, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "Variations in Education Level",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
  scale_fill_manual(values = c( 
    "NET OPPOSE" = "#D2042D", 
    "NET SUPPORT" = "#50C878", 
    "Unsure" = "gray" 
  )) +
  guides(fill = "none") +
   theme_minimal()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

 ggplot(education2, aes(y = Education, x = n, fill = Position)) + 
   geom_col(position = "fill")
```

The support and opposition for the job guarantee is very close between the two groups, however 14% of people with 4 or more years of college are in opposition. People with less education have slightly higher support 79%, only one percentage point higher than the highly educated sample group.

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}
ggplot(education, 
       aes(x = Education, y = Percentage, fill = Education)) + 
  geom_col() + 
  facet_wrap(~Position, labeller = label_wrap_gen(width = 12))
```

## Income

People earning less than \$75K and people earning at least \$75K per year are compared in these graphs.

```{r echo=FALSE, warning=FALSE, message=FALSE}

income <- Hill |> select("<$75k", "$75k+", "Position") |> 
  pivot_longer(!Position,
  names_to = "Income",
  values_to = "Percentage"
)

income <- income |>
  mutate(n = 
           case_when(Income == "<$75k" ~ Percentage*476,
                     Income == "$75k+" ~ Percentage*429,
                    ))
income2 <- income |> filter(Position != "Strongly support") |>
  filter(Position != "Somewhat support") |>
  filter(Position != "Strongly oppose") |>
  filter(Position != "Somewhat oppose") 
 
 ggplot(income2, aes(x = Income, y = Percentage, fill = Income)) +
  geom_col() +
  facet_wrap(~Position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  labs(title = "Variations in Income Level",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
   theme_minimal()
 
 ggplot (income2, aes(x=Income, y=Percentage, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "Variations in Income Level",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
  scale_fill_manual(values = c( 
    "NET OPPOSE" = "#D2042D", 
    "NET SUPPORT" = "#50C878", 
    "Unsure" = "gray" 
  )) +
  guides(fill = "none") +
   theme_minimal()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

 ggplot(income2, aes(y = Income, x = n, fill = Position)) + 
   geom_col(position = "fill")
```

13% of higher earners, compared to 8% of lower earners oppose the job guarantee. 82% of those earning less than \$75K and 77% of those earning at least \$75K support the job guarantee.

## Race

```{r echo=FALSE, warning=FALSE, message=FALSE}

race <- Hill |> select(White, "Black/AA", Hispanic, Position) |> pivot_longer(!Position,
  names_to = "Race",
  values_to = "Percentage"
)

race <- race |>
  mutate(n = 
           case_when(Race == "White" ~ Percentage*634,
                     Race == "Black/AA" ~ Percentage*112,
                     Race == "Hispanic" ~ Percentage*131))


race2 <- race |> filter(Position != "Strongly support") |>
  filter(Position != "Somewhat support") |>
  filter(Position != "Strongly oppose") |>
  filter(Position != "Somewhat oppose")


ggplot(race2, aes(x = Race, y = Percentage, fill = Race)) +
  geom_col() +
  facet_wrap(~Position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  guides(fill = "none") +
  labs(title = "What do racial groups think of the Job Guarantee?",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
  theme_minimal()

ggplot (race2, aes(x=Race, y=Percentage, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "What do racial groups think of the Job Guarantee?",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = NULL, y = NULL) +
  scale_fill_manual(values = c( 
    "NET OPPOSE" = "#D2042D", 
    "NET SUPPORT" = "#50C878", 
    "Unsure" = "gray" 
  )) +
  guides(fill = "none") +
  theme_minimal()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

ggplot(race2, aes(y = Race, x = n, fill = Position)) + 
  geom_col(position = "fill")+
  labs(title = "What do racial groups think of the Job Guarantee?",
       subtitle = "Harris and Hill Survey",
       caption = "The Hill-HarrisX Daily Poll. 2020. Federal Jobs Program.",
       x = "Proportion", y = "Race")
```

The Black sample population has the highest level of support for the job guarantee at 84%, while the Hispanic segment of the sample supports it the least at 74%.

```{r echo=FALSE, warning=FALSE, message=FALSE}


```

## Brexit

The survey results are also diagregated between respondents who believe the UK should have left the EU and those who believe that the UK should not have left the EU.

```{r echo=FALSE, warning=FALSE, message=FALSE}

brexit <- UKYouGov |> select("Remain", "Leave", "Position") |> 
  pivot_longer(!Position,
  names_to = "Opinion",
  values_to = "Percentage"
)

brexit <- brexit |>
  mutate(n = 
           case_when(Opinion == "Remain" ~ Percentage*748,
                     Opinion == "Leave" ~ Percentage*798,
                    ))

brexit <- brexit |> filter(Position != "Very Supportive") |>
  filter(Position != "Supportive") |>
  filter(Position != "Unsupportive") |>
  filter(Position != "Very unsupportive")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}
 
 brexit |>
  mutate(Position = 
  case_when(
    Position == "Neither supportive or unsupportive" ~ "Neutral/Don't Know",
    Position == "Don't know" ~ "Neutral/Don't Know",
    .default = Position
            )) |>
   ggplot(aes(x = Opinion, y = Percentage, fill = Opinion)) +
  geom_col() +
  facet_wrap(~Position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  labs(title = "The Brexit Question",
       subtitle = "UKYouGov Survey",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = NULL, y = NULL) +
   theme_minimal()
 
 ggplot (brexit, aes(x=Opinion, y=Percentage, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5))  +
  labs(title = "The Brexit Question",
       subtitle = "UKYouGov Survey",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = NULL, y = NULL) +
   theme_minimal()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

brexit |>
  mutate(Position = 
  case_when(
    Position == "Neither supportive or unsupportive" ~ "Neutral/Don't Know",
    Position == "Don't know" ~ "Neutral/Don't Know",
    .default = Position
            )) |>
ggplot(aes(y = Opinion, x = n, fill = Position)) + 
   geom_col(position = "fill") +
  labs(title = "The Brexit Question",
       subtitle = "UKYouGov Survey",
       caption = "YouGov Plc. 2020. YouGov / NEON Survey Results.",
       x = NULL, y = NULL) +
  theme_minimal()
```

People in the sample who believe that the UK should have left the EU were more supportive of the job guarantee at 74% support. The people who believe the UK should have remained in the EU oppose the job guarantee at 9%, 3% higher than the 'leave' camp.

```{r echo=FALSE, warning=FALSE, message=FALSE}

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

regionUK |>
  mutate(Position = 
  case_when(
    Position == "Neither supportive or unsupportive" ~ "Neutral/Don't Know",
    Position == "Don't know" ~ "Neutral/Don't Know",
    Position == "Total unsupportive" ~ "Total Unsupportive",
    .default = Position
            )) |>
ggplot(aes(y = Region, x = n, fill = Position)) + 
   geom_col(position = "fill") +
  scale_fill_manual(values = c( 
    "Neutral/Don't Know" = "gray", 
    "Total Supportive" = "#2E8B57", 
    "Total Unsupportive" = "#D2042D" 
  )) +
  theme_minimal()
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

```

## Gender

```{r echo=FALSE, warning=FALSE, message=FALSE}

franceGender <- francePoll |> select(men, women, position) |> 
  pivot_longer(!position,
  names_to = "Gender",
  values_to = "Percentage"
)

franceGender <- franceGender |>
  mutate(n = 
           case_when(Gender == "men" ~ Percentage*483,
                     Gender == "women" ~ Percentage*528,
                    ))

franceGender <- franceGender |> filter(position != "Somewhat in favor") |>
  filter(position != "quite in favor") |>
  filter(position != "Somewhat opposed") |>
  filter(position != "quite opposed")
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

ggplot (franceGender, aes(y=Percentage, x=Gender, fill=position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "Men vs Women",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = NULL, y = NULL, fill = NULL) +
  theme_minimal()
 
 ggplot(franceGender, aes(x = Gender, y = Percentage, fill = Gender)) +
  geom_col() +
  facet_wrap(~position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  labs(title = "Men vs Women",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = NULL, y = NULL) +
   theme_minimal()
```

Women in France support the job guarantee 8% more than men according to this poll. Both groups have majority support for the job guarantee.

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

ggplot(franceGender, aes(y = Gender, x = n, fill = position)) + 
   geom_col(position = "fill") +
  labs(title = "Men vs Women",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = NULL, y = NULL) +
  theme_minimal()

```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

franceCSP <- francePoll |> select(csp, csp_2, inactifs, position) |> pivot_longer(!position,
  names_to = "CSP",
  values_to = "Percentage"
)

franceCSP <- franceCSP |>
  mutate(n = 
           case_when(CSP == "csp" ~ Percentage*283,
                     CSP == "csp_2" ~ Percentage*294,
                     CSP == "inactifs" ~ Percentage*434))

franceCSP <- franceCSP |>
  mutate(CSP =
           case_when(CSP == "csp" ~ "CSP +",
                     CSP == "csp_2" ~ "CSP -",
                     CSP == "inactifs" ~ "Inactifs"
           ))


franceCSP <- franceCSP |> filter(position != "Somewhat in favor") |>
  filter(position != "quite in favor") |>
  filter(position != "Somewhat opposed") |>
  filter(position != "quite opposed")
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

 ggplot(franceCSP, aes(y = CSP, x = n, fill = position)) + 
  geom_col(position = "fill")+
  labs(title = "What do CSP groups think of the job guarantee?",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = "Proportion", y = "CSP status") +
   theme_minimal()

  ggplot(franceCSP, aes(x = CSP, y = Percentage, fill = CSP)) +
  geom_col() +
  facet_wrap(~position, nrow = 2) +
  guides(fill = "none") +
  labs(title = "What do CSP groups think of the job guarantee?",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = NULL, y = NULL) +
    theme_minimal()
```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

ggplot(frenchRegion, aes(y = Region, x = n, fill = position)) + 
   geom_col(position = "fill")

```

## Communities: Rural, Suburban, and Urban

```{r echo=FALSE, warning=FALSE, message=FALSE}

ruralUrbanFrance <- francePoll |> select(rural_community, city_with_2_000_to_19_999_inhabitants, city_with_20_000_to_99_999_inhabitants, city_with_more_than_100_000_inhabitants, greater_paris_region, position) |> 
  pivot_longer(!position,
  names_to = "Community",
  values_to = "Percentage"
)

ruralUrbanFrance <- ruralUrbanFrance |>
  mutate(n = 
           case_when(Community == "rural_community" ~ Percentage*237,
  Community == "city_with_2_000_to_19_999_inhabitants" ~ Percentage*172,
  Community == "city_with_20_000_to_99_999_inhabitants" ~ Percentage*128,
  Community == "city_with_more_than_100_000_inhabitants" ~ Percentage*307,
  Community == "greater_paris_region" ~ Percentage*167
                     ))

ruralUrbanFrance <- ruralUrbanFrance |>
  mutate(Community = case_when(Community == "rural_community" ~ "Rural",
  Community == "city_with_2_000_to_19_999_inhabitants" ~ "Small City",
  Community == "city_with_20_000_to_99_999_inhabitants" ~ "Medium City",
  Community == "city_with_more_than_100_000_inhabitants" ~ "Big City",
  Community == "greater_paris_region" ~ "Greater Paris region"))

ruralUrbanFrance <- ruralUrbanFrance |> filter(position != "Somewhat in favor") |>
  filter(position != "quite in favor") |>
  filter(position != "Somewhat opposed") |>
  filter(position != "quite opposed")

ggplot(ruralUrbanFrance, aes(y = position, x = Percentage, fill = position)) +
  geom_col() +
  facet_wrap(~Community, nrow = 2, labeller = label_wrap_gen(width = 12)) +
  guides(fill = "none") +
  labs(title = "What do French communities think of the job guarantee?",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = "Percentage", y = NULL) +
  scale_fill_manual(values = c(
    "Total opposed" = "#ef8a62", 
    "Total in favor" = "#67a9cf",
    "No response" = "gray"
  )) +
  theme_minimal()

ggplot (ruralUrbanFrance, aes(y=Percentage, x=Community, fill=position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "What do French communities think of the job guarantee?",
       subtitle = "French poll",
       caption = "OpinionWay and Institut Rousseau. March 2021. Survey Results. France",
       x = "Percentage", y = NULL) +
  theme_minimal()

```

```{r echo=FALSE, warning=FALSE, message=FALSE, eval=FALSE}

ggplot(ruralUrbanFrance, aes(y = Community, x = n, fill = position)) + 
   geom_col(position = "fill")
```

Urban and rural areas did not vary greatly in support for the job guarantee. The greater Paris region had the lowest support at 79% in favor and 20% opposed.

```{r echo=FALSE, warning=FALSE, message=FALSE}

genderUS <- Hill |> select(Male, Female, Position) |> 
  filter(Position != "Strongly support") |>
  filter(Position != "Somewhat support") |>
  filter(Position != "Somewhat oppose") |>
  filter(Position != "Strongly oppose") |>
  mutate(Position = case_when(
    Position == "NET SUPPORT" ~ "Total Supportive",
    Position == "Unsure" ~ "Neutral/Don't Know",
    Position == "NET OPPOSE" ~ "Total unsupportive",
    .default = Position))

genderFrance <- francePoll |> select(men, women, position) |> 
  filter(position != "Somewhat in favor") |>
  filter(position != "quite in favor") |>
  filter(position != "Somewhat opposed") |>
  filter(position != "quite opposed") |>
  mutate(Position = case_when(
    position == "Total in favor" ~ "Total Supportive",
    position == "No response" ~ "Neutral/Don't Know",
    position == "Total opposed" ~ "Total unsupportive",
    .default = position))

genderUK <- UKYouGov |> select(Male, Female, Position)|> 
  filter(Position != "Very Supportive") |>
  filter(Position != "Supportive") |>
  filter(Position != "Unsupportive") |>
  filter(Position != "Very unsupportive") |>
  mutate(Position = case_when(
    Position == "Neither supportive or unsupportive" ~ "Neutral/Don't Know",
    Position == "Don't know" ~ "Neutral/Don't Know",
    .default = Position
  ))

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

gender <- full_join(genderUK, genderUS, join_by(Position))
gender <- full_join(gender, genderFrance) 
colnames(gender) <- c("ukm", "ukf", "Position", "usm", "usf", "fm", "ff", "position")
gender <- gender %>% select(-position)

gender <- gender |> 
  pivot_longer(!Position,
  names_to = "Gender",
  values_to = "Percentage"
)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

 ggplot(gender, aes(x = Gender, y = Percentage, fill = Gender)) +
  geom_col() +
  facet_wrap(~Position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  labs(title = "Men vs Women",
       subtitle = "All olls",
       caption = "various sources",
       x = NULL, y = NULL) +
   scale_fill_discrete(labels = 
    c("French Women", "French Men", "UK Women", "UK Men", "US Women", "US Men")) +
   theme_minimal()
 
 ggplot (gender, aes(y=Percentage, x=Gender, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "Men vs Women",
       subtitle = "All polls",
       caption = "various sources",
       x = NULL, y = NULL, fill = NULL) +
   scale_x_discrete(labels = c("French Women", "Men", "UK Women", "UK Men", "US Women", "US Men")) +
   theme_minimal()
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

totalUS <- Hill |> select(Total, Position) |> 
  filter(Position != "Strongly support") |>
  filter(Position != "Somewhat support") |>
  filter(Position != "Somewhat oppose") |>
  filter(Position != "Strongly oppose") |>
  mutate(Position = case_when(
    Position == "NET SUPPORT" ~ "Total Supportive",
    Position == "Unsure" ~ "Neutral/Don't Know",
    Position == "NET OPPOSE" ~ "Total unsupportive",
    .default = Position))

totalFrance <- francePoll |> select(total, position) |> 
  filter(position != "Somewhat in favor") |>
  filter(position != "quite in favor") |>
  filter(position != "Somewhat opposed") |>
  filter(position != "quite opposed") |>
  mutate(Position = case_when(
    position == "Total in favor" ~ "Total Supportive",
    position == "No response" ~ "Neutral/Don't Know",
    position == "Total opposed" ~ "Total unsupportive",
    .default = position))

totalUK <- UKYouGov |> select(Total, Position)|> 
  filter(Position != "Very Supportive") |>
  filter(Position != "Supportive") |>
  filter(Position != "Unsupportive") |>
  filter(Position != "Very unsupportive") |>
  mutate(Position = case_when(
    Position == "Neither supportive or unsupportive" ~ "Neutral/Don't Know",
    Position == "Don't know" ~ "Neutral/Don't Know",
    .default = Position
  ))

totals <- full_join(totalUK, totalUS, join_by(Position))
totals <- full_join(totals, totalFrance) 

```

```{r echo=FALSE, warning=FALSE, message=FALSE}

colnames(totals) <- c("UK", "Position", "US", "France", "position")

totals <- totals %>% select(-position)

totals <- totals |> 
  pivot_longer(!Position,
  names_to = "Total",
  values_to = "Percentage"
)
```

```{r echo=FALSE, warning=FALSE, message=FALSE}

 ggplot(totals, aes(x = Total, y = Percentage, fill = Total)) +
  geom_col() +
  facet_wrap(~Position, nrow = 1, labeller = label_wrap_gen(width = 12)) +
  labs(title = "Country Comparison",
       subtitle = "All polls",
       caption = "various sources",
       x = NULL, y = NULL) +
   theme_minimal()
 
 ggplot (totals, aes(y=Percentage, x=Total, fill=Position)) + 
  geom_bar (stat="identity", position = position_dodge(width = 0.5)) +
  labs(title = "Country Comparison",
       subtitle = "All polls",
       caption = "various sources",
       x = NULL, y = NULL, fill = NULL) +
   theme_minimal()
```

forcats - package

in theme - how to rotate axis labels in ggplot2

viridis, brewer pallates

put don't know and neither together, which group has the most uninformed or unopinionated

make percentages appear differently: specify axis label - specify what the tic marks should be
